todo: think about good title

### 2019-01-04 documentation/paper.tex

%}}}
%{{{ graphics
\usepackage{graphicx} % Bilder
%}}}
%{{{ math
\usepackage{mathrsfs} % mathcal and mathscr
\usepackage{mathtools, amssymb, amsthm}
\usepackage{bm} % cool bold symbols
%}}}
%{{{ a todo command
\newcounter{todocounter}
\newcommand{\todo}[2][noisnotdefined]{
 \marginpar{\fcolorbox{black}{yellow}{\footnotesize\textbf{todo}}
 \ifthenelse{\equal{#1}{noisnotdefined}}{}{\textcolor{black}{\newline\tiny #1}} }
 \textbf{\ifthenelse{\equal{#2}{.}}
   {\fcolorbox{blue}{white}{\textcolor{blue}{$\maltese$} } }{ {\textcolor{blue}{#2} } } }
 \refstepcounter{todocounter} }
%}}}

@@

@@

\begin{figure}
\begin{tabular}{c|ccccccc}
vs. & 
\texttt{ Axji-0-2 } &
\texttt{ COM\_11 } &
\texttt{ GintonicV9 } &
\texttt{ Hypo14 } &
\texttt{ reduced } &
\texttt{ Union } &
\texttt{ trainer } \\
\hline
\texttt{ Axji-0-2 } & - & 0 & 0 & 4 & 0 & 0 & 10 \\
\texttt{ COM\_11 } & 21 & - & 9 & 19 & 6 & 16 & 20 \\
\texttt{ GintonicV9 } & 21 & 12 & - & 19 & 6 & 16 & 20 \\
\texttt{ Hypo14 } & 17 & 2 & 2 & - & 2 & 5 & 15 \\
\texttt{ reduced } & 21 & 19 & 15 & 19 & - & 19 & 21 \\
\texttt{ Union } & 21 & 14 & 5 & 16 & 2 & - & 20 \\
\texttt{ trainer } & 11 & 0 & 1 & 6 & 0 & 1 & -
\end{tabular}
\caption{scores of bots competing against each other}
\end{figure}

@@

@@

@@

@@

@@

@@

Parameter tuning may be needed.

@@

@@

>>>>

%}}}
%{{{ graphics
\usepackage{graphicx} % Bilder
\usepackage{tikz, pgfplots}
\pgfplotsset{compat=1.14}
%}}}
%{{{ math
\usepackage{mathrsfs} % mathcal and mathscr
\usepackage{mathtools, amssymb, amsthm}
\usepackage{bm} % cool bold symbols
%}}}
% a todo command===============================================================
\usepackage[ruled]{algorithm2e}
\newcounter{todocounter}
\newcommand{\todo}[2][noisnotdefined]{
 \marginpar{\fcolorbox{black}{orange}{\footnotesize\textbf{todo}}
 \ifthenelse{\equal{#1}{noisnotdefined}}{}{\textcolor{black}{\newline\tiny #1}}}
 \textbf{\ifthenelse{\equal{#2}{.}}
   {\fcolorbox{orange}{white}{\textcolor{orange}{$\maltese$}}}{{\textcolor{orange}{#2}}}}
 \refstepcounter{todocounter}}

%===============================================================================

@@

\todo{include reference \cite{Garis90geneticprogramming} (beginning of neuroevolution, cited by Sims)}
\todo{include reference \cite{Sims94evolving3d} (Sims himself)}

@@

\begin{figure}[H]
\begin{tabular}{c|ccccccc}
vs. & 
\texttt{ Axji-0-2 } &
\texttt{ COM\_11 } &
\texttt{ GintonicV9 } &
\texttt{ Hypo14 } &
\texttt{ reduced } &
\texttt{ Union } &
\texttt{ trainer } \\
\hline
\texttt{ Axji-0-2 } & - & 0 & 0 & 4 & 0 & 0 & 10 \\
\texttt{ COM\_11 } & 21 & - & 9 & 19 & 6 & 16 & 20 \\
\texttt{ GintonicV9 } & 21 & 12 & - & 19 & 6 & 16 & 20 \\
\texttt{ Hypo14 } & 17 & 2 & 2 & - & 2 & 5 & 15 \\
\texttt{ reduced } & 21 & 19 & 15 & 19 & - & 19 & 21 \\
\texttt{ Union } & 21 & 14 & 5 & 16 & 2 & - & 20 \\
\texttt{ trainer } & 11 & 0 & 1 & 6 & 0 & 1 & -
\end{tabular}
\caption{scores of bots competing against each other}
\end{figure}

\todo{explain the table}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/standard.png}
\caption{trained bots against all other}
\label{fig:standard}
\end{figure}

\todo{coclusion: bots too hard we therefore reward gameplay by the *\_5t bots}

\todo{introduce the goal of an overall good bot and explain the plot along the way (added fitnesses (score of 12 would mean winneing every point against every bot))}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/standard_5t.png}
\caption{trained bots against all other}
\label{fig:standard_5t}
\end{figure}

\todo{conclusion: better, and not only for 5t bots (algorithm has something to grab on)}

\todo{overall: not very pretty graphs -> need self adaption}

@@

\todo{explain what we are doing}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_1.png}
\caption{trained bots against all other}
\label{fig:self_adapt_1}
\end{figure}

\todo{we can see that the algorithm is converging}
\todo{because trainer is beatable, the nn has something to grab on and performs way better thatn the others}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2_5t.png}
\caption{trained bots against all other}
\label{fig:self_adapt_2_5t}
\end{figure}

\todo{now it's pretty}
\todo{trainer\_5t bad because it is very easy to beat and therefore we can get loast in a local optimum real quick}

@@

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2.png}
\caption{trained bots against all other}
\label{fig:self_adapt_2}
\end{figure}

\todo{similar to section before without 5t}

@@

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_adapt_2_5t.png}
\caption{trained bots against all other}
\label{fig:self_adapt_2_5t}
\end{figure}

\todo{not very predictable behaviour}
\todo{works good for a few examples}
\todo{remember prof has never seen this stuff working and will be happy if it has disadvantages}

\section{Changing opponent}

200 gen \texttt{gintonicV9\_5t}, 200 gen \texttt{com\_11\_5t}, 200 gen \texttt{gintonicV9}, 200 gen \texttt{com\_11}.
\todo{argument with the previous plots that this is a good idea}
\todo{other ideas?}

\begin{figure}[H]
\center
\begin{tabular}{ccc}
standard & self adapt 1 & self adapt 2 \\
\includegraphics[width=0.3\textwidth]{img/standard_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_2_gintonicV9_5t_com_11_5t_gintonicV9_com_11.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:changing opponent}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/change.png}
\caption{trained bots against all other}
\label{fig:change}
\end{figure}

\todo{only self adapt 1 works}
\todo{we could do more with more generations but loose the comparebility to the previous section}

\section{Self-training}

\subsection{last best}

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_1.png}
\caption{Scheme for self training variant 1}
\label{fig:scheme_self_training_1}
\end{figure}

Fitness evaluated with the best bot of the last generation.

\begin{figure}[H]
\center
\begin{tabular}{cc}
standard & self adapt 1\\
\includegraphics[width=0.3\textwidth]{img/standard_last_best.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_last_best.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum.}
\label{fig:last_best}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=0.3\textwidth]{img/self_training_1.png}
\caption{trained bots against all other}
\label{fig:self_training_1}
\end{figure}

\todo{risk to end up in local optimum like self adapt 1?}

\subsection{two species}

\begin{figure}[H]
\center
\includegraphics[width=0.155555\textwidth]{img/scheme_self_training_1.png}
\caption{Scheme for self training variant 1}
\label{fig:scheme_self_training_2}
\end{figure}

\begin{figure}[H]
\center
\begin{tabular}{cc}
left side & right side \\
\includegraphics[width=0.3\textwidth]{img/standard_self_training_2_1.png} &
\includegraphics[width=0.3\textwidth]{img/standard_self_training_2_2.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum standard mutation.}
\label{fig:standard_self_training_2}
\end{figure}

\todo{too much diversity}

\begin{figure}[H]
\center
\begin{tabular}{cc}
left side & right side \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_1_oldrun.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_2_oldrun.png}
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum with self adapt 1.}
\label{fig:self_adapt_1_self_training_2_oldrun}
\end{figure}

\todo{sadly they do not change too often}
\todo{there is still improvement even though it can not be seen in the plots because they improve themselves}

\begin{figure}[H]
\center
\begin{tabular}{cc}
left side & right side \\
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_1.png} &
\includegraphics[width=0.3\textwidth]{img/self_adapt_1_self_training_2_2.png} \\
\end{tabular}
\caption{Fitness density with indicated minimum, average and maximum with self adapt 1 and more generations.}
\label{fig:self_adapt1_self_training_2}
\end{figure}

\begin{figure}[H]
\center
\includegraphics[width=0.4\textwidth]{img/self_training_2.png}
\caption{trained bots against all other}
\label{fig:self_training_2}
\end{figure}

\todo{we got a pretty awesome bot there which gets beaten only by reduced but never trained against it}

\section{Discussion and Future Ideas}

\todo{everything we have not done}
\todo{train the self trained bot with reduced so we maybe get a perfect score of 12}
\todo{we have not used too many inputs I still coudn't beat the bot which trained itself for four hours}
\todo{acknowledgement to the compute server}
